Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-20 cordillera-cycle.tex
Actually update record table and change notation.
I had forgotten to do it in the last commit. Use bracket notation for mean temperature anomaly from 32 to 22 ka.

\begin{table*}
\caption{%
      Palaeo-temperature proxy records and scaling parameters yielding
      temperature offset time-series used to force the ice sheet model
      through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$ corresponds
      to the scaling factor adopted to yield last glacial maximum ice limits
      in the vicinity of mapped end moraines, and $T_{[32, 22]}$ refers to
      the resulting mean temperature anomaly during the period $-$32
      to~$-$22\,\unit{ka} after scaling.}
\label{tab:records}
%\scalebox{.850}[.850]
{\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (\unit{m\,a.s.l.}) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.37 & $-$5.8  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree}06$^{\prime}$\,N   % 75.10
             &  42{\degree}19$^{\prime}$\,W   % 42.32
             & 2917
             & \chem{\delta^{18}O}
             & 0.24 & $-$6.5  % -26.7098
             & \citet{Andersen.etal.2004} \\

@@

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.74 & $-$5.9  % -7.9550
             & \citet{Petit.etal.1999} \\

@@

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & $-$3038
             & \chem{U^{K'}_{37}}
             & 1.20 & $-$6.0 % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}

>>>>

\begin{table*}
\caption{%
      Palaeo-temperature proxy records and scaling parameters yielding
      temperature offset time-series used to force the ice sheet model
      through the last glacial cycle (Fig.~\ref{fig:lr_ts}). $f$ corresponds
      to the scaling factor adopted to yield last glacial maximum ice limits
      in the vicinity of mapped end moraines, and
      $[{\Delta}T_{\text{TS}}]_{32}^{22}$ refers to the resulting mean
      temperature anomaly during the period 32 to~22\,\unit{ka} after
      scaling.}
\label{tab:records}
%\scalebox{.850}[.850]
{\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev.
           & Proxy & $f$ & $[{\Delta}T_{\text{TS}}]_{32}^{22}$
           & Reference\\
    & & & (\unit{m\,a.s.l.}) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
             &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
             & 3238
             & \chem{\delta^{18}O}
             & 0.38 & $-$6.2  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree}06$^{\prime}$\,N   % 75.10
             &  42{\degree}19$^{\prime}$\,W   % 42.32
             & 2917
             & \chem{\delta^{18}O}
             & 0.25 & $-$6.6  % -26.7098
             & \citet{Andersen.etal.2004} \\

@@

    Vostok   &  78{\degree}28$^{\prime}$\,S   % 78.8
             & 106{\degree}50$^{\prime}$\,E   % 106.8
             & 3488
             & \chem{\delta^{18}O}
             & 0.75 & $-$6.0  % -7.9550
             & \citet{Petit.etal.1999} \\

@@

    ODP~1020 &  41{\degree}00$^{\prime}$\,N
             & 126{\degree}26$^{\prime}$\,W
             & $-$3038
             & \chem{U^{K'}_{37}}
             & 1.18 & $-$5.9  % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
\end{tabular}}
\end{table*}
